---
title: "Final Project Analysis" 
author: "Yousuf Kanan and Derek Allmon"
output: html_notebook
---

```{r include=FALSE}
library(tidyverse)
library(infer)
```

```{r include=FALSE}
# Load the data
cudaFloatMult = read_csv("Cuda/Cudafloat_mult.csv")
#make sure to change both variables to doubles
cudaFloatMult$Time = as.double(cudaFloatMult$Time)
cudaFloatMult$Size = as.double(cudaFloatMult$Size)
cudaFloatAdd = read_csv("Cuda/CudaFloat.csv")
cudaFloatAdd$Time = as.double(cudaFloatAdd$Time)
cudaFloatAdd$Size = as.double(cudaFloatAdd$Size)
cudaDoubleAdd = read_csv("Cuda/CudaSize_double.csv")
cudaDoubleAdd$Time = as.double(cudaDoubleAdd$Time)
cudaDoubleAdd$Size = as.double(cudaDoubleAdd$Size)
cudaDoubleMult = read_csv("Cuda/CudaSize_mult_double.csv")
cudaDoubleMult$Time = as.double(cudaDoubleMult$Time)
cudaDoubleMult$Size = as.double(cudaDoubleMult$Size)
```



```{r echo=FALSE}
cudaFloatMult %>% ggplot(aes(x = Size, y = Time)) +
  geom_point() + geom_smooth() + ggtitle("Float Multiplication") + xlab("Size") + ylab("Time")

```


```{r echo=FALSE}
cudaDoubleMult %>% ggplot(aes(x = Size, y = Time)) +
  geom_point() + geom_smooth() + ggtitle("Double Multiplication") + xlab("Size") + ylab("Time")
```

The two graphs Double Multiplication and Float Multiplication show a linear relationship between the size and time. As expected the float multiplication is faster than the double multiplication because the float multiplication is more efficient on a GPU.


```{r echo=FALSE, warning=FALSE}
cudaFloatAdd %>% ggplot(aes(x = Size, y = Time)) +
  geom_point() + geom_smooth() + ggtitle("Float Addition") + xlab("Size") + ylab("Time")
```

```{r echo=FALSE}

cudaDoubleAdd %>% ggplot(aes(x = Size, y = Time)) +
  geom_point() + geom_smooth() + ggtitle("Double Addition") + xlab("Size") + ylab("Time")


```


The two graphs Double Addition and Float Addition show a linear relationship between the size and time. As expected the float addition is faster than the double addition because the float addition is more efficient on a GPU.


Although the float addition and multiplication are faster than the double addition and multiplication, the difference is not as significant as we expected. 



